Individual Differenes

### 2023-08-24 Analysis/Appendix/E1_Appendix.qmd
re-render + update plot functions

```{r setupAe1, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

modelName <- "e1_testDistBand_RF_5K_Ml1"
e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)

e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k_Ml1")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))

>>>>

```{r setupAe1, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)

modelName <- "e1_testDistBand_RF_5K"
e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)

e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))

### 2023-08-24 Analysis/e1_test.qmd
re-render + update plot functions

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

modelName <- "e1_testDistBand_RF_5K_Ml1"
e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)
mp1 <- GetModelStats(e1_distBMM) |> kable(escape=F,booktabs=T)
mp1
```

@@

```{r}
#| label: tbl-e1-bmm-vx
#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k_Ml1")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)

@@

```{r}

```{r}
#| label: fig-e1-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
#| layout-ncol: 2
e1_vxBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +

@@

indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e1Sbjs, by=join_by(id) ) |> 
  group_by(condit) |> 
  mutate(rank = rank(desc(Estimate.bandInt)),
         intErrorRank=rank((Est.Error.Intercept)),
         bandErrorRank=rank((Est.Error.bandInt)),
         nCond = n()) |> arrange(intErrorRank)

@@

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 2000) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

@@

combined_df <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id"),relationship="many-to-many") |> 
  mutate(
    fixed_effects = b_Intercept +
      (bandInt * b_bandInt) +
      condit_dummy * b_conditVaried + 
      (bandInt * condit_dummy) * `b_conditVaried:bandInt` ,  # Note: Replace : with correct operator
    random_effects = Intercept + bandInt_RF,  # Assuming random effects for intercept and bandInt
    estimate = fixed_effects + random_effects
  )

@@

>>>>

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-21-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e1Sbjs <- test |> group_by(id,condit) |> summarise(n=n())
testAvg <- test %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

modelName <- "e1_testDistBand_RF_5K"
e1_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=test,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)
GetModelStats(e1_distBMM) |> kable(escape=F,booktabs=T)

@@

```{r}
#| label: tbl-e1-bmm-vx
#| tbl-cap: "Experiment 1. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
#| tbl-subcap: ["Model fit to all 6 bands", "Model fit to 3 extrapolation bands"]
e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)

@@

```{r}
#| label: fig-e1-bmm-vx
#| fig-cap: Conditional effect of training condition and Band. Ribbons indicate 95% HDI. The steepness of the lines serves as an indicator of how well participants discriminated between velocity bands. 
#| fig-subcap: ["Model fit to all 6 bands", "Model fit to only 3 extrapolation bands"]
#| layout-ncol: 2

condEffectsPlot <- ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
  scale_x_continuous(breaks = c(100, 350, 600), 
                     labels = levels(test$vb)[1:3], 
                     limits = c(0, 1000)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

e1_vxBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() + stat_halfeye(alpha=.2) +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +

@@

indv_coefs <- coef(e1_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e1Sbjs, by=join_by(id) ) |> 
  group_by(condit) |> 
  mutate(rank = rank(desc(Estimate.bandInt)),
         intErrorRank=rank((Est.Error.Intercept)),
         bandErrorRank=rank((Est.Error.bandInt)),
         nCond = n()) |> arrange(intErrorRank) |> ungroup()

@@

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

@@

combined_df <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    fixed_effects = b_Intercept +
      (bandInt * b_bandInt) +
      condit_dummy * b_conditVaried + 
      (bandInt * condit_dummy) * `b_conditVaried:bandInt` ,  
    random_effects = Intercept + bandInt_RF,  # Assuming random effects for intercept and bandInt
    estimate = (b_Intercept + Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`
  )

@@

combined_df |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=4,"max")
combined_df |> indv_model_plot(indv_coefs, testAvg, rank_variable=Estimate.bandInt,n_sbj=4,"min")

### 2023-08-24 Misc/indv_diff.qmd
re-render + update plot functions

e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k_Ml1")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
mt2 <-GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)

>>>>

e1_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=test,file=paste0(here::here("data/model_cache", "e1_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
mt2 <-GetModelStats(e1_vxBMM ) |> kable(escape=F,booktabs=T)
